EagerNet: Early Predictions of Neural Networks for Computationally Efficient Intrusion Detection

### 2020-07-21 paper/paper.tex
Minor cosmetic changes

\glspl{ffnn} have been the basis of most state-of-the-art \gls{ml} applications in recent years. Experiments show that the deeper the network is, the more desirable it is to acquire more knowledge. Nonetheless, with the growing number of layers, obtaining fast predictions has become a difficult task despite the use of special hardware such as GPUs. We propose a new architecture to obtain predictions without conducting a forward-pass until the last layer. The architecture is able to deal with either binary or multiclass classification problems and trades prediction speed for the confidence of the network. We evaluate our proposal with two different network intrusion detection datasets. Results suggest that it is possible to obtain comparable accuracies to simple \glspl{ffnn} without evaluating all layers, thus obtaining early predictions and saving energy and computational efforts.

@@

\section{Introduction}
% what are ffnn
\glspl{ffnn} have gained remarkable attention in recent years due to the availability of data and computational resources for research. Many of the state-of-the-art architectures currently used in different applications are effectively based on simple \glspl{ffnn} architectures. Experiments show that the more layers (and neurons) the network includes, the more desirable it is for better learning \cite{eldan2016power} .

@@

	\footnotesize
	\begin{tabular}{ccc}
		\toprule
		\textbf{Direction}                    & \textbf{Features}        & \textbf{Statistical Operations}        \\
		\midrule

@@

\section{Evaluation and Discussion}
\label{evaluation_and_discussion}
We discuss in this section different experimental results and observations. Overall, EagerNet shows promising performance comparable to \glspl{ffnn} with the ability to save resources.

>>>>

\glspl{ffnn} have been the core of most state-of-the-art \gls{ml} applications in recent years specifically \glspl{ids}. Experiments show that the deeper the network is, the more desirable it is to acquire more knowledge. Nonetheless, with the growing number of layers, obtaining fast predictions with less resources has become a difficult task despite the use of special hardware such as GPUs. We propose a new architecture to detect network attacks with minimal resources. The architecture is able to deal with either binary or multiclass classification problems and trades prediction speed for the accuracy of the network. We evaluate our proposal with two different network intrusion detection datasets. Results suggest that it is possible to obtain comparable accuracies to simple \glspl{ffnn} without evaluating all layers, thus obtaining early predictions and saving energy and computational efforts.

@@

\section{Introduction}
% what are ffnn
\glspl{ffnn} have gained remarkable attention in recent years due to the availability of data and computational resources for research. Many state-of-the-art architectures currently used in different applications are effectively based on simple \glspl{ffnn} architectures. Experiments show that the more layers (and neurons) the network includes, the more desirable it is for better learning \cite{eldan_power_2016} .

@@

	\footnotesize
	\resizebox{\columnwidth}{!}{
	\begin{tabular}{|c|c|c|}
		\toprule
		\textbf{Direction}                    & \textbf{Features}        & \textbf{Statistical Operations}        \\
		\midrule

@@

\section{Evaluation and Discussion}
\label{evaluation_and_discussion}
We discuss in this section different experimental results and observations. Overall, EagerNet shows promising performance comparable to \glspl{ffnn} with the ability to save resources. all experiments are reproducible and available on our repository\footnote{github.com/CN-TU/ids-backdoor/tree/eager}.
